---
title: "Fixation Count Poisson - RawData - IN"
author: "Hanna Stoffregen"
date: "28 Mai 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

# Prepare workspace and data

- **moderator attention:** is calculated using total looking time duration for each subject over entire experimental session
- **moderator free recall and hits (recognition):** are calculated using subject's total score over all picture types

```{r}
#clears workspace:  
#rm(list=ls(all=TRUE))  
```
```{r}
## Functions 

### write function to detach all packages to avoid interferences
detachAllPackages <- function() { 
  #store basic packages names in a list
  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:dataSets","package:methods","package:base")  
  #make list of all loaded packages
  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]
  #remove basic packages from the list
  package.list <- setdiff(package.list,basic.packages)
  #remove all packages from the list
  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)
}
### write function to detect outliers for boxplots
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}
```
```{r}
## Load required libraries
library(ggplot2)
library(glmm)
library(lme4)
library(reshape2)
library(plyr)
library(dplyr)
library(foreign)
library(ez)
library(pastecs)
library(knitr)
library(ggpubr)
```
```{r}
## Data collection and preparation
#save path to main directory
path="C:/Users/BAN7836/Documents/NadiaMA/DataAnalysis"
#change working directory to data directory
setwd(paste(path,"/Data", sep=""))
#read in spss file and create data set
dataSet  <-  read.spss("MA_Nadia_Ramos_1800508_ALL_DATA_Hanna.sav", to.data.frame=T)
```
```{r, settings for dataframe creation}
#define attention score
attentionDefine <- "FreeRecall"
#should within subjects variables be adjusted?
adjust <- FALSE
#should scores be related to group mean?
relateScores <- FALSE
#for lm: define reference group
ref <- "IN"
```
```{r, exclude subjects}
### data exclusion
#exclude subjects (see exclusion criteria Nadia)
df <- dataSet[!(dataSet$vpn %in% c(3,6,17,20,41,64,73)), ]
```
```{r, prepare data}
### data preparation
#melt dataframe for TimeToFirstFixation + make three seperate variables for picture group number (1-9), order (6 possible), TypeOfInterest (which pictureType A, B or C the TTFF refers to)
dummyDf <- melt(df, measure.vars = c(27:132), variable.name = "pictureType", value.name = "TTFF")
dummyDf$Picture <- substr(dummyDf$pictureType,21,21)
dummyDf$Order <- substr(dummyDf$pictureType,22,23)
dummyDf$Type <- substr(dummyDf$pictureType, 29,29)
dummyDf$Picture <- as.factor(dummyDf$Picture)
dummyDf$Order <- as.factor(dummyDf$Order)
dummyDf$Type <- as.factor(dummyDf$Type)

#extract FixationDurationData
FixDura <- df[, c(1, 133:238)]
#melt dataframe for FixationDuration
FixDura <- melt(FixDura, measure.vars = c(2:107), variable.name = "pictureType1", value.name = "FixationDuration")
FixDura$Picture <- substr(FixDura$pictureType,18,18)
FixDura$Order <- substr(FixDura$pictureType,19,20)
FixDura$Type <- substr(FixDura$pictureType, 26,26)
FixDura$Picture <- as.factor(FixDura$Picture)
FixDura$Order <- as.factor(FixDura$Order)
FixDura$Type <- as.factor(FixDura$Type)


#extract FixationCount
FixCount <- df[, c(1, 239:344)]
#melt dataframe for FixationCount
FixCount <- melt(FixCount, measure.vars = c(2:107), variable.name = "pictureType2", value.name = "FixationCount")
FixCount$Picture <- substr(FixCount$pictureType,15,15)
FixCount$Order <- substr(FixCount$pictureType,16,17)
FixCount$Type <- substr(FixCount$pictureType, 23,23)
FixCount$Picture <- as.factor(FixCount$Picture)
FixCount$Order <- as.factor(FixCount$Order)
FixCount$Type <- as.factor(FixCount$Type)

df <- merge(dummyDf, FixDura)
df <- merge(df, FixCount)

#rename factor Type and relevel so that X is reference
df$Type <- mapvalues(df$Type, from = c("g", "n", "o"), to = c("A", "X","B"))
df$Type <- relevel(df$Type, ref="B")

# relevel bedingung, so that MC is referene
df$bedingung <- mapvalues(df$bedingung, from = c("Indulging", "MC"), to = c("IN", "MC"))

if (ref == "MC"){
  df$bedingung <- relevel(df$bedingung, ref="MC")
} else if (ref=="IN"){
  df$bedingung <- relevel(df$bedingung, ref="IN")
}

# create dataframe with only relevant data
df <- df[,c(1:4,6,10:11,28,588,590,592, 587, 570:574)]
df$pictureType <- gsub("TimetoFirstFixation_", "", df$pictureType)
df$pictureType <- gsub("_Mean", "", df$pictureType)
df$pictureType <- gsub(".jpg", "", df$pictureType)

#create attention score
dummyDf <- df[!is.na(df$FixationDuration),]
dummyAttention <- dummyDf %>% group_by(vpn) %>% summarize(attention = sum(FixationDuration))
df <- merge(df, dummyAttention, by = "vpn")
#create free recall score
df$freeRecall <- df$FANTASIEREL + df$HINDERNISREL + df$NEUTRAL
#create hit score
df$Hits <- df$Recog_Fantasie + df$Recog_Hindernis

#remove recall variables to keep column indices the same
df <- df[, -c(13:17)]

#adjust variables and relate to total score of vp

df$grandMean <- NA
df[c(df$bedingung=="MC"),]$grandMean <- mean(df[c(df$bedingung=="MC"),]$FixationCount, na.rm=T)
df[c(df$bedingung=="IN"),]$grandMean <- mean(df[c(df$bedingung=="IN"),]$FixationCount, na.rm=T)
df$pMean <- NA

for (i in c(unique(df$vpn))){
  df[c(df$vpn==i),]$pMean <- mean(df[c(df$vpn==i),]$FixationCount, na.rm=T)
}
df$adj <- df$grandMean - df$pMean

if (adjust == TRUE){
  df$FixationCount <- df$FixationCount - df$adj
}

#relate scores to mean in group
if (relateScores == TRUE){
 df$FixationCount <- df$FixationCount/df$grandMean
}

#delete dummy variables
df <- df[,-c(16:18)]

# DERIVATIVE DATAFRAMES OF DF (dfDiff for difference scores, dfLM and dfDiffLM for linear models)

#create new df that contains difference scores (A-X, B-X, A-B) rather than single scores
dfDiff <- dcast(df,  vpn+Picture+Order+bedingung+erwartung+anreiz+commitment+attention+freeRecall+Hits ~ Type, value.var = "FixationCount", mean)
dfDiff$A[is.nan(dfDiff$A_fantasy)] <- NA
dfDiff$B[is.nan(dfDiff$B_obstacle)] <- NA
dfDiff$X[is.nan(dfDiff$X_neutral)] <- NA

dfDiff$Ax <- dfDiff$A - dfDiff$X
dfDiff$Bx <- dfDiff$B - dfDiff$X
dfDiff$AB <- dfDiff$A - dfDiff$B

dfDiff <- melt(dfDiff, measure.vars = c(14:16), variable.name = "DiffScore", value.name = "FixationCount")
#rename Order
dfDiff$Order <- mapvalues(dfDiff$Order, from = c("AX", "XA", "BX", "XB", "AB", "BA"), to = c("minLeft", "minRight","minLeft", "minRight", "minLeft", "minRight"))
#delete unnecesarry variables
dfDiff <- dfDiff[,-c(11:13)]

# create dfLM for linear models on single scores with centralized moderators (on mean)
# centralize all moderators in dfLM

dfLM <- df
manreiz <- mean(dfLM$anreiz, na.rm=TRUE)
merwartung <- mean(dfLM$erwartung, na.rm=TRUE)
mcommitment <- mean(dfLM$commitment, na.rm=TRUE)
mattention <- mean(dfLM$attention, na.rm=TRUE)
mfreeRecall <- mean(dfLM$freeRecall, na.rm=TRUE)
mHits <- mean(df$Hits, na.rm=TRUE)

dfLM$anreiz <- dfLM$anreiz - manreiz
dfLM$erwartung <- dfLM$erwartung - merwartung
dfLM$commitment <- dfLM$commitment - mcommitment
dfLM$attention <- dfLM$attention - mattention
dfLM$freeRecall <- dfLM$freeRecall - mfreeRecall
dfLM$Hits <- dfLM$Hits - mHits
# create dfDiff for linear models on difference scores with centralized moderators (on mean)

# centralize moderators in df Diff

dfDiffLM <- dfDiff
manreiz <- mean(dfDiffLM$anreiz, na.rm=TRUE)
merwartung <- mean(dfDiffLM$erwartung, na.rm=TRUE)
mcommitment <- mean(dfDiffLM$commitment, na.rm=TRUE)
mattention <- mean(dfDiffLM$attention, na.rm=TRUE)
mfreeRecall <- mean(dfDiffLM$freeRecall, na.rm=TRUE)
mHits <- mean(dfDiff$Hits, na.rm=TRUE)

dfDiffLM$anreiz <- dfDiffLM$anreiz - manreiz
dfDiffLM$erwartung <- dfDiffLM$erwartung - merwartung
dfDiffLM$commitment <- dfDiffLM$commitment - mcommitment
dfDiffLM$attention <- dfDiffLM$attention - mattention
dfDiffLM$freeRecall <- dfDiffLM$freeRecall - mfreeRecall
dfDiffLM$Hits <- dfDiffLM$Hits - mHits

```
```{r}
# Settings
# name y axis for graphs

xname = "Time To First Fixation"
xnameDiff = "DiffScore Time To First Fixation \n (negative values = minuend was looked at first)"

```

# Data Exploration/Outlier Detection

## Single Scores

### Scatterplot for single scores for individual pictures (1-9)

```{r, fig.width=15, fig.height = 6}
Graph <- df
Graph <- Graph[!is.na(Graph$FixationCount),]

Graph <- Graph %>%
    group_by(Picture, Order, bedingung, Type) %>%
    summarise(mean.FixationCount = mean(FixationCount), sd.FixationCount = sd(FixationCount), se.FixationCount = sd(FixationCount)/sqrt(n()), n=n()) 

gp <- ggplot(data = Graph,
             aes(x=Type, y=mean.FixationCount, colour=Order))
#set points
gp <- gp + geom_point()
gp <- gp + facet_grid(bedingung~Picture)
#set x-axis label
gp <- gp + xlab("A(fantasy), B(obstacle), X(neutral) - Picture Numbers 1-9")
#set y-axis label
gp <- gp + ylab(xname)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#show plot
gp
```

### Boxplot: detect outlier picture groups

```{r}

Graph <- Graph %>%
  group_by(bedingung, Type, Order) %>%
  mutate(outlier = ifelse(is_outlier(mean.FixationCount),Picture, as.numeric(NA))) 

```
```{r, fig.width = 12}
gp <- ggplot(data = Graph,
             aes(x=Order, y=mean.FixationCount, colour=bedingung))
#set points
gp <- gp + geom_boxplot()
gp <- gp + facet_wrap(~Type)
gp <- gp + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Order")
#set y-axis label
gp <- gp + ylab(xname)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#set title
gp <- gp + ggtitle(paste("Outlier Pics for Condition  "))
#show plot
gp
```

### Scatterplot: check difference scores aggregated over subjects

```{r, fig.width=12, fig.height=9}
Graph <- dfDiff
Graph <- Graph[!is.na(Graph$FixationCount),]

Graph <- Graph %>%
    group_by(Picture, bedingung, DiffScore, Order) %>%
    summarise(mean.FixationCount = mean(FixationCount), sd.FixationCount = sd(FixationCount), se.FixationCount = sd(FixationCount)/sqrt(n()), n=n())

gp <- ggplot(data = Graph,
             aes(x=Picture, y=mean.FixationCount, colour=bedingung))
#set points
gp <- gp + geom_point()
gp <- gp + facet_grid(Order~DiffScore)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Number of Picture")
#set y-axis label
gp <- gp + ylab(xnameDiff)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#gp <- gp + ggtitle(paste("Pulse at TSST for each Pps"))
#show plot
gp
```

### Boxplot: detect outlier picture groups

```{r}

Graph <- Graph %>%
  group_by(bedingung, DiffScore, Order) %>%
  mutate(outlier = ifelse(is_outlier(mean.FixationCount),Picture, as.numeric(NA))) 

```
```{r, fig.width = 12}
gp <- ggplot(data = Graph,
             aes(x=Order, y=mean.FixationCount, colour=bedingung))
#set points
gp <- gp + geom_boxplot()
gp <- gp + facet_wrap(~DiffScore)
gp <- gp + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Order")
#set y-axis label
gp <- gp + ylab(xnameDiff)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#show plot
gp
```

# Data Analysis with single scores

## simple spearman correlations (Anreiz, Erwartung, Commitment, Attention, Free Recall, Recognition (Hits))


```{r}
#df1 <- df %>%
  #group_by(vpn, Type, anreiz, bedingung) %>%
  #summarise(FixationCount = mean(FixationCount, na.rm=T)) 
```
```{r, fig.width = 12, fig.height = 6}
gp <- ggplot(df, aes(anreiz, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "spearman")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Anreiz", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(erwartung, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "spearman")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Erwartung", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(commitment, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "spearman")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Commitment", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(attention, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "spearman")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Attention", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(freeRecall, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "spearman")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "freeRecall", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(Hits, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "spearman")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Hits", y=xname)
gp <- gp + theme_minimal() 
gp

```

## General Linear Models with poisson distribution

### GLM with Bedingung + Type

```{r}
dfLM$FixationCount[is.nan(dfLM$FixationCount)] <- NA
dfLM <- dfLM[!is.na(dfLM$FixationCount),]

model <- glm(FixationCount ~ bedingung*Type, family = poisson(), data=dfLM)

summary(model)
```

### GLM Moderator Analysis

- *note that moderator variables are centered at the sample mean for meaningful interpretation of main effects*

#### Anreiz

```{r}
model <- glm(FixationCount ~ bedingung*Type*anreiz, family=poisson(), data=dfLM)
summary(model)
```

#### Commitment

```{r}
model <- glm(FixationCount ~ bedingung*Type*commitment, family=poisson(), data=dfLM)
summary(model)
```

#### Erwartung

```{r}
model <- glm(FixationCount ~ bedingung*Type*erwartung, family=poisson(), data=dfLM)
summary(model)
```

#### Attention

```{r}
model <- glm(FixationCount ~ bedingung*Type*attention, family=poisson(), data=dfLM)
summary(model)
```

#### Free Recall

```{r}
model <- glm(FixationCount ~ bedingung*Type*freeRecall, family=poisson(), data=dfLM)
summary(model)
```

#### Recognition - Hits

```{r}
model <- glm(FixationCount ~ bedingung*Type*Hits, family=poisson(), data=dfLM)
summary(model)
```

# Data Analysis with DiffScores

## simple spearman correlations (Anreiz, Erwartung, Commitment, Attention, Free Recall, Hits)

### Line Graphs Displaying Correlations

```{r, fig.width = 12, fig.height = 6}
gp <- ggplot(dfDiff, aes(anreiz, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Anreiz", y=xnameDiff)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(dfDiff, aes(erwartung, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Erwartung", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(commitment, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Commitment", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(attention, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Attention", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(freeRecall, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Free Recall", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(Hits, FixationCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Recognition-Hits", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  


```

## Linear Models on Difference Scores

### Fantasy (A) - Neutral (X)

#### Simple Model

```{r}
dfDiffLM <- dfDiffLM[!is.na(dfDiff$FixationCount),]
dfDiffLM <- dcast(dfDiffLM,  vpn+Picture+bedingung+erwartung+anreiz+commitment+Order+attention+freeRecall+Hits ~ DiffScore, value.var = "FixationCount", mean)

dfDiffLM$Ax[is.nan(dfDiffLM$Ax)] <- NA

model <- lm(Ax ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(Ax ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(Ax ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(Ax ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(Ax ~ bedingung*Order*attention, data=dfDiffLM)
model5 <- lm(Ax ~ bedingung*Order*freeRecall, data=dfDiffLM)
model6 <- lm(Ax ~ bedingung*Order*Hits, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```

#### Free Recall

```{r}
summary(model5)
```

#### Recognition - Hits

```{r}
summary(model6)
```

### Obstacle (B) - Neutral (X)

#### Simple Model

```{r}
dfDiffLM$Bx[is.nan(dfDiffLM$Bx)] <- NA

model <- lm(Bx ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(Bx ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(Bx ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(Bx ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(Bx ~ bedingung*Order*attention, data=dfDiffLM)
model5 <- lm(Bx ~ bedingung*Order*freeRecall, data=dfDiffLM)
model6 <- lm(Bx ~ bedingung*Order*Hits, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```

#### Free Recall

```{r}
summary(model5)
```

#### Recognition - Hits

```{r}
summary(model6)
```

### Fantasy (A) - Obstacle (B)

#### Simple Model

```{r}
dfDiffLM$AB[is.nan(dfDiffLM$AB)] <- NA

model <- lm(AB ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(AB ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(AB ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(AB ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(AB ~ bedingung*Order*attention, data=dfDiffLM)
model5 <- lm(AB ~ bedingung*Order*freeRecall, data=dfDiffLM)
model6 <- lm(AB ~ bedingung*Order*Hits, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```

#### Free Recall

```{r}
summary(model5)
```

#### Recognition - Hits

```{r}
summary(model6)
```