---
title: "Free Recall - IN"
author: "Hanna Stoffregen"
date: "23 Mai 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

# Prepare workspace and data

```{r}
#clears workspace:  
#rm(list=ls(all=TRUE))  
```
```{r}
## Functions 

### write function to detach all packages to avoid interferences
detachAllPackages <- function() { 
  #store basic packages names in a list
  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:dataSets","package:methods","package:base")  
  #make list of all loaded packages
  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]
  #remove basic packages from the list
  package.list <- setdiff(package.list,basic.packages)
  #remove all packages from the list
  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)
}
### write function to detect outliers for boxplots
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}
```
```{r}
## Load required libraries
library(ggplot2)
library(glmm)
library(lme4)
library(reshape2)
library(plyr)
library(dplyr)
library(foreign)
library(ez)
library(pastecs)
library(knitr)
library(ggpubr)
```
```{r}
## Data collection and preparation
#save path to main directory
path="C:/Users/BAN7836/Documents/NadiaMA/DataAnalysis"
#change working directory to data directory
setwd(paste(path,"/Data", sep=""))
#read in spss file and create data set
dataSet  <-  read.spss("MA_Nadia_Ramos_1800508_ALL_DATA_Hanna.sav", to.data.frame=T)
```
```{r}
### data exclusion
#exclude subjects (see exclusion criteria Nadia)
df <- dataSet[!(dataSet$vpn %in% c(3,6,17,20,41,64,73)), ]
```
```{r}
### data preparation
#melt dataframe for TimeToFirstFixation + make three seperate variables for picture group number (1-9), order (6 possible), TypeOfInterest (which pictureType A, B or C the TTFF refers to)
dummyDf <- melt(df, measure.vars = c(27:132), variable.name = "pictureType", value.name = "TTFF")
dummyDf$Picture <- substr(dummyDf$pictureType,21,21)
dummyDf$Order <- substr(dummyDf$pictureType,22,23)
dummyDf$Type <- substr(dummyDf$pictureType, 29,29)
dummyDf$Picture <- as.factor(dummyDf$Picture)
dummyDf$Order <- as.factor(dummyDf$Order)
dummyDf$Type <- as.factor(dummyDf$Type)

#extract FixationDurationData
FixDura <- df[, c(1, 133:238)]
#melt dataframe for FixationDuration
FixDura <- melt(FixDura, measure.vars = c(2:107), variable.name = "pictureType1", value.name = "FixationDuration")
FixDura$Picture <- substr(FixDura$pictureType,18,18)
FixDura$Order <- substr(FixDura$pictureType,19,20)
FixDura$Type <- substr(FixDura$pictureType, 26,26)
FixDura$Picture <- as.factor(FixDura$Picture)
FixDura$Order <- as.factor(FixDura$Order)
FixDura$Type <- as.factor(FixDura$Type)


#extract FixationCount
FixCount <- df[, c(1, 239:344)]
#melt dataframe for FixationCount
FixCount <- melt(FixCount, measure.vars = c(2:107), variable.name = "pictureType2", value.name = "FixationCount")
FixCount$Picture <- substr(FixCount$pictureType,15,15)
FixCount$Order <- substr(FixCount$pictureType,16,17)
FixCount$Type <- substr(FixCount$pictureType, 23,23)
FixCount$Picture <- as.factor(FixCount$Picture)
FixCount$Order <- as.factor(FixCount$Order)
FixCount$Type <- as.factor(FixCount$Type)

df <- merge(dummyDf, FixDura)
df <- merge(df, FixCount)

#rename factor Type and relevel so that X is reference
df$Type <- mapvalues(df$Type, from = c("g", "n", "o"), to = c("A", "X","B"))
df$Type <- relevel(df$Type, ref="B")

# relevel bedingung, so that MC is referene
df$bedingung <- mapvalues(df$bedingung, from = c("Indulging", "MC"), to = c("IN", "MC"))

df$bedingung <- relevel(df$bedingung, ref="IN")



# create dataframe with only relevant data
df <- df[,c(1:4,6,10:11,28,588,590,592,587,570:574)]
df$pictureType <- gsub("TimetoFirstFixation_", "", df$pictureType)
df$pictureType <- gsub("_Mean", "", df$pictureType)
df$pictureType <- gsub(".jpg", "", df$pictureType)

# create an attention score with FixationDuration
dummyDf <- df[!is.na(df$FixationDuration),]
dummyAttention <- dummyDf %>% group_by(vpn) %>% summarize(attention = sum(FixationDuration))

#attach attention variable to df
df <- merge(df, dummyAttention, by = "vpn")

#include Memory scores (free recall and recognition)

df$recallCount <- NA
df[df$Type == "A",]$recallCount <- df[df$Type == "A",]$FANTASIEREL
df[df$Type == "B",]$recallCount <- df[df$Type == "B",]$HINDERNISREL
df[df$Type == "X",]$recallCount <- df[df$Type == "X",]$NEUTRAL

df$recognition <- NA
df[df$Type == "A",]$recognition <- df[df$Type == "A",]$Recog_Fantasie
df[df$Type == "B",]$recognition <- df[df$Type == "B",]$Recog_Hindernis

df <- within(df, rm("FANTASIEREL", "HINDERNISREL", "NEUTRAL", "Recog_Fantasie", "Recog_Hindernis"))

# DERIVATIVE DATAFRAMES OF DF (dfDiff for difference scores, dfLM and dfDiffLM for linear models)

#create new df that contains difference scores (A-X, B-X, A-B) rather single scores
dfDiff <- dcast(df,  vpn+Picture+Order+bedingung+erwartung+anreiz+commitment+attention ~ Type, value.var = "recallCount", mean)
dfDiff$A[is.nan(dfDiff$A_fantasy)] <- NA
dfDiff$B[is.nan(dfDiff$B_obstacle)] <- NA
dfDiff$X[is.nan(dfDiff$X_neutral)] <- NA

dfDiff$Ax <- dfDiff$A - dfDiff$X
dfDiff$Bx <- dfDiff$B - dfDiff$X
dfDiff$AB <- dfDiff$A - dfDiff$B

dfDiff <- melt(dfDiff, measure.vars = c(12:14), variable.name = "DiffScore", value.name = "recallCount")
#rename Order
dfDiff$Order <- mapvalues(dfDiff$Order, from = c("AX", "XA", "BX", "XB", "AB", "BA"), to = c("minLeft", "minRight","minLeft", "minRight", "minLeft", "minRight"))
#delete unnecesarry variables
dfDiff <- dfDiff[,-c(9:11)]

# create dfLM for linear models on single scores with centralized moderators (on mean)
# centralize all moderators in dfLM

dfLM <- df
manreiz <- mean(dfLM$anreiz, na.rm=TRUE)
merwartung <- mean(dfLM$erwartung, na.rm=TRUE)
mcommitment <- mean(dfLM$commitment, na.rm=TRUE)
mattention <- mean(dfLM$attention, na.rm=TRUE)

dfLM$anreiz <- dfLM$anreiz - manreiz
dfLM$erwartung <- dfLM$erwartung - merwartung
dfLM$commitment <- dfLM$commitment - mcommitment
dfLM$attention <- dfLM$attention - mattention

# create dfDiff for linear models on difference scores with centralized moderators (on mean)

# centralize moderators in df Diff

dfDiffLM <- dfDiff
manreiz <- mean(dfDiffLM$anreiz, na.rm=TRUE)
merwartung <- mean(dfDiffLM$erwartung, na.rm=TRUE)
mcommitment <- mean(dfDiffLM$commitment, na.rm=TRUE)
mattention <- mean(dfDiffLM$attention, na.rm=TRUE)

dfDiffLM$anreiz <- dfDiffLM$anreiz - manreiz
dfDiffLM$erwartung <- dfDiffLM$erwartung - merwartung
dfDiffLM$commitment <- dfDiffLM$commitment - mcommitment
dfDiffLM$attention <- dfDiffLM$attention - mattention
```
```{r}
# Settings
# name y axis for graphs

xname = "Recall"
xnameDiff = "DiffScore Recall\n (positive values = minuend was recalled better)"

```

# Data Exploration/Outlier Detection

## Single Scores

### Scatterplot for single scores for individual pictures (1-9)

```{r, fig.width=15, fig.height = 6}
Graph <- df
Graph <- Graph[!is.na(Graph$recallCount),]

Graph <- Graph %>%
    group_by(vpn, bedingung, Type) %>%
    summarise(mean.recallCount = mean(recallCount), sd.recallCount = sd(recallCount), se.recallCount = sd(recallCount)/sqrt(n()), n=n()) 

gp <- ggplot(data = Graph,
             aes(x=vpn, y=mean.recallCount, colour=bedingung))
#set points
gp <- gp + geom_point()
gp <- gp + facet_wrap(~Type)
#set x-axis label
gp <- gp + xlab("Subject")
#set y-axis label
gp <- gp + ylab(xname)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#show plot
gp
```

### Boxplot: detect outlier picture groups

```{r}

Graph <- Graph %>%
  group_by(vpn, bedingung, Type) %>%
  mutate(outlier = ifelse(is_outlier(mean.recallCount),vpn, as.numeric(NA))) 

```
```{r, fig.width = 12}
gp <- ggplot(data = Graph,
             aes(x=Type, y=mean.recallCount, colour=bedingung))
#set points
gp <- gp + geom_boxplot()
gp <- gp + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Type")
#set y-axis label
gp <- gp + ylab(xname)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#set title
gp <- gp + ggtitle(paste("Outlier Subjects for Condition"))
#show plot
gp
```

### Scatterplot: check difference scores for all subjects

```{r, fig.width=12, fig.height=9}
Graph <- dfDiff
Graph <- Graph[!is.na(Graph$recallCount),]

Graph <- Graph %>%
    group_by(vpn, bedingung, DiffScore) %>%
    summarise(mean.recallCount = mean(recallCount), sd.recallCount = sd(recallCount), se.recallCount = sd(recallCount)/sqrt(n()), n=n())

gp <- ggplot(data = Graph,
             aes(x=vpn, y=mean.recallCount, colour=bedingung))
#set points
gp <- gp + geom_point()
gp <- gp + facet_wrap(~DiffScore)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("subject")
#set y-axis label
gp <- gp + ylab(xnameDiff)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#gp <- gp + ggtitle(paste("Pulse at TSST for each Pps"))
#show plot
gp
```

- Similar to eye tracking data, i.e., better recall for AB compared to X

### Boxplot: detect outlier picture groups

```{r}

Graph <- Graph %>%
  group_by(vpn, bedingung, DiffScore) %>%
  mutate(outlier = ifelse(is_outlier(mean.recallCount),vpn, as.numeric(NA))) 

```
```{r, fig.width = 12}
gp <- ggplot(data = Graph,
             aes(x=DiffScore, y=mean.recallCount, colour=bedingung))
#set points
gp <- gp + geom_boxplot()
gp <- gp + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Order")
#set y-axis label
gp <- gp + ylab(xnameDiff)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#show plot
gp
```

# Data Analysis with single scores

## simple spearman correlations (Anreiz, Erwartung, Commitment)

```{r, fig.width = 12, fig.height = 6}
gp <- ggplot(df, aes(anreiz, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~Type)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Anreiz", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(commitment, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~Type)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Commitment", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(erwartung, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~Type)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Erwartung", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(attention, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~Type)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Attention", y=xname)
gp <- gp + theme_minimal() 
gp
```

#### Comments on correlations

- Anreiz correlated positiviely with MC/B, negatively with MC+IN/A+X
- Erwartung for Indulging negative correlations for B, positive for A, for MC positive for X
- Commitment: MC positive correlations for A and B, IN positive correlation for X
- Attention: IN positve correlations for A and B, for MC only for B


## GLM with Bedingung + Type and Poisson Distribution

```{r}
dfLM$recallCount[is.nan(dfLM$recallCount)] <- NA
dfLM <- dfLM[!is.na(dfLM$recallCount),]
model2 <- glm(recallCount ~ bedingung + Type + bedingung*Type, family = poisson(), data=dfLM)

summary(model2)
```

## LM Moderator Analysis

### Anreiz

```{r}
model2 <- glm(recallCount ~ bedingung + Type + anreiz + bedingung*Type + bedingung*anreiz + Type*anreiz + bedingung*Type*anreiz, family=poisson(), data=dfLM)
summary(model2)
```

### Commitment

```{r}
model2 <- glm(recallCount ~ bedingung + Type + commitment + bedingung*Type + bedingung*commitment + Type*commitment + bedingung*Type*commitment, family=poisson(), data=dfLM)
summary(model2)

```

- IN looked less often at B
- MC looked less often at X than B
- commitment decreases looking counts for In group in B
- for X this decrease is significanty lower

### Erwartung

```{r}
model2 <- glm(recallCount ~ bedingung + Type + erwartung + bedingung*Type + bedingung*erwartung + Type*erwartung + bedingung*Type*erwartung, family=poisson(), data=dfLM)
summary(model2)
```

### Attention

```{r}
model2 <- glm(recallCount ~ bedingung + Type + attention + bedingung*Type + bedingung*attention + Type*attention + bedingung*Type*attention, family=poisson(), data=dfLM)
summary(model2)
```

# Data Analysis with DiffScores

## Line Graphs Displaying spearman Correlations

```{r, fig.width = 12, fig.height = 6}
gp <- ggplot(dfDiff, aes(anreiz, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Anreiz", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(dfDiff, aes(commitment, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Commitment", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(dfDiff, aes(erwartung, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Erwartung", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(dfDiff, aes(attention, recallCount, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_wrap(~DiffScore)
gp <- gp + stat_cor(method = "spearman")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Attention", y=xname)
gp <- gp + theme_minimal() 
gp

```

## LM with Anreiz, Erwartung, Commitment, Attention on DiffScores

### Fantasy (A) - Neutral (X)

```{r}
dfDiffLM <- dfDiffLM[!is.na(dfDiffLM$recallCount),]
dfDiffLM <- dcast(dfDiffLM,  vpn+Picture+bedingung+erwartung+anreiz+commitment+Order+attention ~ DiffScore, value.var = "recallCount", mean)

dfDiffLM$Ax[is.nan(dfDiffLM$Ax)] <- NA

model <- lm(Ax ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(Ax ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(Ax ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(Ax ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(Ax ~ bedingung*Order*attention, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```


### Obstacle (B) - Neutral (X)

```{r}
dfDiffLM$Bx[is.nan(dfDiffLM$Bx)] <- NA

model <- lm(Bx ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(Bx ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(Bx ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(Bx ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(Bx ~ bedingung*Order*attention, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```

### Fantasy - Obstacle

```{r}
dfDiffLM$AB[is.nan(dfDiffLM$AB)] <- NA

model <- lm(AB ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(AB ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(AB ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(AB ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(AB ~ bedingung*Order*attention, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```