---
title: "Total Fixation Duration - raw scores"
author: "Hanna Stoffregen"
date: "28 Mai 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

# Prepare workspace and data

-	**NOT corrected for within subjects variables picture, Type, and Order:** adjustment factor (= group mean - individual mean) is subtracted from raw scores
-	**scores are NOT given as a relation to total scores per group:** individual score(s)/group mean
- **moderator attention:** is calculated using total looking time duration for each subject over entire experimental session
- **moderator free recall and hits (recognition):** are calculated using subject's total score over all picture types

```{r}
#clears workspace:  
#rm(list=ls(all=TRUE))  
```
```{r}
## Functions 

### write function to detach all packages to avoid interferences
detachAllPackages <- function() { 
  #store basic packages names in a list
  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:dataSets","package:methods","package:base")  
  #make list of all loaded packages
  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]
  #remove basic packages from the list
  package.list <- setdiff(package.list,basic.packages)
  #remove all packages from the list
  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)
}
### write function to detect outliers for boxplots
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}
```
```{r}
## Load required libraries
library(ggplot2)
library(glmm)
library(lme4)
library(reshape2)
library(plyr)
library(dplyr)
library(foreign)
library(ez)
library(pastecs)
library(knitr)
library(ggpubr)
library(yarrr)
```
```{r}
## Data collection and preparation
#save path to main directory
setwd("../Data")
tf <- read.table("MA_Nadia_Ramos_Total_Fixation_Duration_include_zeros.txt", , sep = "\t", header = T)
#read in spss file and create data set
dataSet  <-  read.spss("MA_Nadia_Ramos_1800508_ALL_DATA_Hanna.sav", to.data.frame=T)

df <- join(dataSet, tf, by = "vpn")
```

```{r, settings for dataframe creation}
#should within subjects variables be adjusted?
adjust <- F
#should scores be related to group mean?
relateScores <- F
#for lm: define reference group
ref <- "MC"
```
```{r, exclude subjects}
### data exclusion
#exclude subjects (see exclusion criteria Nadia)
df <- df[!(df$vpn %in% c(3,6,17,20,41,64,73)), ]
```
```{r, prepare data}
### data preparation
#melt dataframe for TimeToFirstFixation + make three seperate variables for picture group number (1-9), order (6 possible), TypeOfInterest (which pictureType A, B or C the TTFF refers to)
dummyDf <- melt(df, measure.vars = c(27:132), variable.name = "pictureType", value.name = "TTFF")
dummyDf$Picture <- substr(dummyDf$pictureType,21,21)
dummyDf$Order <- substr(dummyDf$pictureType,22,23)
dummyDf$Type <- substr(dummyDf$pictureType, 29,29)
dummyDf$Picture <- as.factor(dummyDf$Picture)
dummyDf$Order <- as.factor(dummyDf$Order)
dummyDf$Type <- as.factor(dummyDf$Type)

#extract FixationDurationData
FixDura <- df[, c(1, 133:238)]
#melt dataframe for FixationDuration
FixDura <- melt(FixDura, measure.vars = c(2:107), variable.name = "pictureType1", value.name = "FixationDuration")
FixDura$Picture <- substr(FixDura$pictureType,18,18)
FixDura$Order <- substr(FixDura$pictureType,19,20)
FixDura$Type <- substr(FixDura$pictureType, 26,26)
FixDura$Picture <- as.factor(FixDura$Picture)
FixDura$Order <- as.factor(FixDura$Order)
FixDura$Type <- as.factor(FixDura$Type)

#extract FixationCount
FixCount <- df[, c(1, 239:344)]
#melt dataframe for FixationCount
FixCount <- melt(FixCount, measure.vars = c(2:107), variable.name = "pictureType2", value.name = "FixationCount")
FixCount$Picture <- substr(FixCount$pictureType,15,15)
FixCount$Order <- substr(FixCount$pictureType,16,17)
FixCount$Type <- substr(FixCount$pictureType, 23,23)
FixCount$Picture <- as.factor(FixCount$Picture)
FixCount$Order <- as.factor(FixCount$Order)
FixCount$Type <- as.factor(FixCount$Type)

#extract TotalFixationDurationData
TotalFixDura <- df[, c(1, 693:798)]
#melt dataframe for FixationDuration
TotalFixDura <- melt(TotalFixDura, measure.vars = c(2:107), variable.name = "pictureType1", value.name = "TotalFixationDuration")
TotalFixDura$Picture <- substr(TotalFixDura$pictureType,12,12)
TotalFixDura$Order <- substr(TotalFixDura$pictureType,14,16)
TotalFixDura$Type <- substr(TotalFixDura$pictureType, 18,18)
TotalFixDura$Picture <- as.factor(TotalFixDura$Picture)
TotalFixDura$Order <- as.factor(TotalFixDura$Order)
TotalFixDura$Type <- as.factor(TotalFixDura$Type)
TotalFixDura$Order <- mapvalues(TotalFixDura$Order, from = c("A_B", "A_X", "B_A", "B_X", "X_A", "X_B"), to = c("AB", "AX", "BA", "BX", "XA", "XB"))


df <- join(dummyDf, FixDura, by = c("vpn", "Picture", "Order", "Type"))
df <- join(df, FixCount, by = c("vpn", "Picture", "Order", "Type"))
df <- join(df, TotalFixDura, by = c("vpn", "Picture", "Order", "Type"))

#rename factor Type and relevel so that X is reference
df$Type <- mapvalues(df$Type, from = c("g", "n", "o"), to = c("A", "X","B"))
df$Type <- relevel(df$Type, ref="B")

# relevel bedingung, so that MC is referene
df$bedingung <- mapvalues(df$bedingung, from = c("Indulging", "MC"), to = c("IN", "MC"))

if (ref == "MC"){
  df$bedingung <- relevel(df$bedingung, ref="MC")
} else if (ref=="IN"){
  df$bedingung <- relevel(df$bedingung, ref="IN")
}

```
```{r}
# create dataframe with only relevant data
df <- df[,c(1, 3, 7, 8, 22:25, 456, 457, 567:571, 690:694, 696, 698, 700)]
df$pictureType <- gsub("TimetoFirstFixation_", "", df$pictureType)
df$pictureType <- gsub("_Mean", "", df$pictureType)
df$pictureType <- gsub(".jpg", "", df$pictureType)

df$TotalFixationDuration <- gsub(",", ".", df$TotalFixationDuration)
df$TotalFixationDuration <- as.numeric(df$TotalFixationDuration)

#create attention score
df$TotalFixationDuration <- as.numeric(df$TotalFixationDuration)
dummyDf <- df[!is.na(df$TotalFixationDuration),]
dummyAttention <- dummyDf %>% dplyr::group_by(vpn) %>% dplyr::summarize(attention = sum(TotalFixationDuration))
df <- join(df, dummyAttention, by = "vpn")
#create free recall score
df$freeRecall <- df$FANTASIEREL + df$HINDERNISREL + df$NEUTRAL
#create hit score
df$Hits <- df$Recog_Fantasie + df$Recog_Hindernis

#remove recall variables to keep column indices the same
#df <- df[, -c(13:17)]
```

```{r, data aggregation}
#df <- df %>%
  #group_by(vpn, bedingung, Type, anreiz, erwartung, commitment, attention, freeRecall, Hits) %>%
  #summarise(FixationDuration = mean(FixationDuration, na.rm=T)) 
```

```{r, data adjustment}
#adjust variables and relate to total score of vp
df$grandMean <- mean(df[c(df$bedingung=="MC"),]$TotalFixationDuration, na.rm=T)
df[c(df$bedingung=="IN"),]$grandMean <- mean(df[c(df$bedingung=="IN"),]$TotalFixationDuration, na.rm=T)

df$pMean = NA
for (i in c(unique(df$vpn))){
  df[c(df$vpn==i),]$pMean <- mean(df[c(df$vpn==i),]$TotalFixationDuration, na.rm=T)
}
df$adj <- df$grandMean - df$pMean

if (adjust == TRUE){
  df$TotalFixationDuration <- df$TotalFixationDuration + df$adj
}

#relate scores to mean in group
if (relateScores == TRUE){
 df$TotalFixationDuration <- df$TotalFixationDuration/df$grandMean
}

#delete dummy variables
#df <- df[,-c(16:18)]
```
# data selection
```{r, data selection}
# give overview over selection variable
pirateplot(formula = TotalFixationDuration ~ anreiz, data = df, theme = 1, main = "Relationship Anreiz - Fixation Duration")
print(summary(df$TotalFixationDuration))

#print(c("choose all pps with fixDura > 350"))

#data selection
#select vp with high anreiz (median split)
#df <- df[c(df$TotalFixationDuration > .35),]
```

```{r, derivative dataframes}
# DERIVATIVE DATAFRAMES OF DF (dfDiff for difference scores, dfLM and dfDiffLM for linear models)

#create new df that contains difference scores (A-X, B-X, A-B) rather than single scores
dfDiff <- dcast(df,  vpn+Picture+Order+bedingung+erwartung+anreiz+commitment+attention+freeRecall+Hits ~ Type, value.var = "TotalFixationDuration", mean)
dfDiff$A[is.nan(dfDiff$A_fantasy)] <- NA
dfDiff$B[is.nan(dfDiff$B_obstacle)] <- NA
dfDiff$X[is.nan(dfDiff$X_neutral)] <- NA

dfDiff$Ax <- dfDiff$A - dfDiff$X
dfDiff$Bx <- dfDiff$B - dfDiff$X
dfDiff$AB <- dfDiff$A - dfDiff$B

dfDiff <- melt(dfDiff, measure.vars = c(14:16), variable.name = "DiffScore", value.name = "TotalFixationDuration")
#rename Order
dfDiff$Order <- mapvalues(dfDiff$Order, from = c("AX", "XA", "BX", "XB", "AB", "BA"), to = c("minLeft", "minRight","minLeft", "minRight", "minLeft", "minRight"))
#delete unnecesarry variables
dfDiff <- dfDiff[,-c(11:13)]

# create dfLM for linear models on single scores with centralized moderators (on mean)
# centralize all moderators in dfLM

dfLM <- df
manreiz <- mean(dfLM$anreiz, na.rm=TRUE)
merwartung <- mean(dfLM$erwartung, na.rm=TRUE)
mcommitment <- mean(dfLM$commitment, na.rm=TRUE)
mattention <- mean(dfLM$attention, na.rm=TRUE)
mfreeRecall <- mean(dfLM$freeRecall, na.rm=TRUE)
mHits <- mean(df$Hits, na.rm=TRUE)

dfLM$anreiz <- dfLM$anreiz - manreiz
dfLM$erwartung <- dfLM$erwartung - merwartung
dfLM$commitment <- dfLM$commitment - mcommitment
dfLM$attention <- dfLM$attention - mattention
dfLM$freeRecall <- dfLM$freeRecall - mfreeRecall
dfLM$Hits <- dfLM$Hits - mHits
# create dfDiff for linear models on difference scores with centralized moderators (on mean)

# centralize moderators in df Diff

dfDiffLM <- dfDiff
manreiz <- mean(dfDiffLM$anreiz, na.rm=TRUE)
merwartung <- mean(dfDiffLM$erwartung, na.rm=TRUE)
mcommitment <- mean(dfDiffLM$commitment, na.rm=TRUE)
mattention <- mean(dfDiffLM$attention, na.rm=TRUE)
mfreeRecall <- mean(dfDiffLM$freeRecall, na.rm=TRUE)
mHits <- mean(dfDiff$Hits, na.rm=TRUE)

dfDiffLM$anreiz <- dfDiffLM$anreiz - manreiz
dfDiffLM$erwartung <- dfDiffLM$erwartung - merwartung
dfDiffLM$commitment <- dfDiffLM$commitment - mcommitment
dfDiffLM$attention <- dfDiffLM$attention - mattention
dfDiffLM$freeRecall <- dfDiffLM$freeRecall - mfreeRecall
dfDiffLM$Hits <- dfDiffLM$Hits - mHits
```

```{r, names fpr axes in graphs}
# name y axis for graphs

xname = "Total Fixation Duration"
xnameDiff = "DiffScore Total Fixation Duration \n (positive values = minuend was looked at longer)"
```
# Data Exploration/Outlier Detection

## Single Scores

### Scatterplot for single scores for individual pictures (1-9)

```{r, fig.width=15, fig.height = 6}
Graph <- df
Graph <- Graph[!is.na(Graph$TotalFixationDuration),]

Graph <- Graph %>%
    group_by(Picture, Order, bedingung, Type) %>%
    summarise(mean.TotalFixationDuration = mean(TotalFixationDuration), sd.TotalFixationDuration = sd(TotalFixationDuration), se.TotalFixationDuration = sd(TotalFixationDuration)/sqrt(n()), n=n()) 

gp <- ggplot(data = Graph,
             aes(x=Type, y=mean.TotalFixationDuration, colour=Order))
#set points
gp <- gp + geom_point()
gp <- gp + facet_grid(bedingung~Picture)
#set x-axis label
gp <- gp + xlab("A(fantasy), B(obstacle), X(neutral) - Picture Numbers 1-9")
#set y-axis label
gp <- gp + ylab(xname)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#show plot
gp
```

### Boxplot: detect outlier picture groups

```{r}

Graph <- Graph %>%
  group_by(bedingung, Type, Order) %>%
  mutate(outlier = ifelse(is_outlier(mean.TotalFixationDuration),Picture, as.numeric(NA))) 

```
```{r, fig.width = 12}
gp <- ggplot(data = Graph,
             aes(x=Order, y=mean.TotalFixationDuration, colour=bedingung))
#set points
gp <- gp + geom_boxplot()
gp <- gp + facet_wrap(~Type)
gp <- gp + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Order")
#set y-axis label
gp <- gp + ylab(xname)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#set title
gp <- gp + ggtitle(paste("Outlier Pics for Condition  "))
#show plot
gp
```

### Scatterplot: check difference scores aggregated over subjects

```{r, fig.width=12, fig.height=9}
Graph <- dfDiff
Graph <- Graph[!is.na(Graph$TotalFixationDuration),]

Graph <- Graph %>%
    group_by(Picture, bedingung, DiffScore, Order) %>%
    summarise(mean.TotalFixationDuration = mean(TotalFixationDuration), sd.TotalFixationDuration = sd(TotalFixationDuration), se.TotalFixationDuration = sd(TotalFixationDuration)/sqrt(n()), n=n())

gp <- ggplot(data = Graph,
             aes(x=Picture, y=mean.TotalFixationDuration, colour=bedingung))
#set points
gp <- gp + geom_point()
gp <- gp + facet_grid(Order~DiffScore)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Number of Picture")
#set y-axis label
gp <- gp + ylab(xnameDiff)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#gp <- gp + ggtitle(paste("Pulse at TSST for each Pps"))
#show plot
gp
```

### Boxplot: detect outlier picture groups

```{r}

Graph <- Graph %>%
  group_by(bedingung, DiffScore, Order) %>%
  mutate(outlier = ifelse(is_outlier(mean.TotalFixationDuration),Picture, as.numeric(NA))) 

```
```{r, fig.width = 12}
gp <- ggplot(data = Graph,
             aes(x=Order, y=mean.TotalFixationDuration, colour=bedingung))
#set points
gp <- gp + geom_boxplot()
gp <- gp + facet_wrap(~DiffScore)
gp <- gp + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
#set x-axis label
gp <- gp + xlab("Order")
#set y-axis label
gp <- gp + ylab(xnameDiff)
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#show plot
gp
```

# Data Analysis with single scores

## simple pearson correlations (Anreiz, Erwartung, Commitment, Attention, Free Recall, Recognition (Hits))

```{r, fig.width = 12, fig.height = 6}
gp <- ggplot(df, aes(anreiz, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "pearson")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Anreiz", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(erwartung, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "pearson")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Erwartung", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(commitment, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "pearson")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Commitment", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(attention, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "pearson")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Attention", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(freeRecall, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "pearson")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "freeRecall", y=xname)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(df, aes(Hits, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
gp <- gp+facet_wrap(~Type)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
#calculate correlations
gp <- gp + stat_cor(method = "pearson")
#set theme and labels
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Hits", y=xname)
gp <- gp + theme_minimal() 
gp

```

## Linear Models 

### LM with Bedingung + Type

```{r}
dfLM$TotalFixationDuration[is.nan(dfLM$TotalFixationDuration)] <- NA
dfLM <- dfLM[!is.na(dfLM$TotalFixationDuration),]

model <- lmer(TotalFixationDuration ~ bedingung*Type + (1 + Type|vpn), data = df)
#dfLM$erwartung <- dfLM$erwartung^2
dfAggregate <- df %>%
  group_by(vpn, bedingung, Type) %>% summarise(mean.TotalFixationDuration = mean(TotalFixationDuration), sd.TotalFixationDuration =
                                                        sd(TotalFixationDuration), se.TotalFixationDuration = sd(TotalFixationDuration)/sqrt(n()), n=n())
ANOVA = ezANOVA(data = dfAggregate, dv = mean.TotalFixationDuration, wid = vpn, within = Type, between = bedingung)

dfAggregateWide <- dfAggregate[,-c(5:7)]
dfAggregateWide <- dcast(dfAggregate, vpn+bedingung ~ Type, value.var = "mean.TotalFixationDuration")

dfAggregateWide$A_X <- dfAggregateWide$A - dfAggregateWide$X
dfAggregateWide$B_X <- dfAggregateWide$B - dfAggregateWide$X
dfAggregateWide$B_A <- dfAggregateWide$B - dfAggregateWide$A

ANOVA_A_X = ezANOVA(data = dfAggregateWide, dv = A_X, wid = vpn, between = bedingung)
ANOVA_B_X = ezANOVA(data = dfAggregateWide, dv = B_X, wid = vpn, between = bedingung)
ANOVA_B_A = ezANOVA(data = dfAggregateWide, dv = B_A, wid = vpn, between = bedingung)

t_A_X <- t.test(dfAggregateWide[c(dfAggregateWide$bedingung == "IN"),]$A_X, dfAggregateWide[c(dfAggregateWide$bedingung == "MC"),]$A_X) 
t_B_X <- t.test(dfAggregateWide[c(dfAggregateWide$bedingung == "IN"),]$B_X, dfAggregateWide[c(dfAggregateWide$bedingung == "MC"),]$B_X)
t_B_A <- t.test(dfAggregateWide[c(dfAggregateWide$bedingung == "IN"),]$B_A, dfAggregateWide[c(dfAggregateWide$bedingung == "MC"),]$B_A)

tB <- t.test(dfAggregateWide[c(dfAggregateWide$bedingung == "IN"),]$B, dfAggregateWide[c(dfAggregateWide$bedingung == "MC"),]$B, alternative = "less") #p = .096
tA <- t.test(dfAggregateWide[c(dfAggregateWide$bedingung == "IN"),]$A, dfAggregateWide[c(dfAggregateWide$bedingung == "MC"),]$A)
tX <- t.test(dfAggregateWide[c(dfAggregateWide$bedingung == "IN"),]$X, dfAggregateWide[c(dfAggregateWide$bedingung == "MC"),]$X)

dftest <- df %>%
  group_by(bedingung, Type, Picture) %>% summarise(mean.TotalFixationDuration = mean(TotalFixationDuration))

dftestwide <- dcast(dftest, Type+Picture ~ bedingung, value.var = "mean.TotalFixationDuration")
dftestwide$value <- dftestwide$MC - dftestwide$IN

ANOVA_diff = ezANOVA(data = dftestwide, dv = value, wid = Picture, between = Type)

t1 <- t.test(dftestwide[c(dftestwide$Type == "B"),]$value, dftestwide[c(dftestwide$Type == "A"),]$value, alternative = "greater") 
t2 <- t.test(dftestwide[c(dftestwide$Type == "B"),]$value, dftestwide[c(dftestwide$Type == "X"),]$value, alternative = "greater") 
t3 <- t.test(dftestwide[c(dftestwide$Type == "A"),]$value, dftestwide[c(dftestwide$Type == "X"),]$value, alternative = "greater") 

p.adjust(c( 0.006, 0.007, 0.61), method = "holm")


#model <- lm(B_A ~ bedingung, data=dfAggregateWide)
#summary(model)

#t.test

#sumTable <- df %>%
  group_by(bedingung, Type) %>% summarise(mean.TotalFixationDuration = mean(TotalFixationDuration), sd.TotalFixationDuration = sd(TotalFixationDuration), 
                                          se.TotalFixationDuration = sd(TotalFixationDuration)/sqrt(n()), n=n())


pirateplot(formula = value ~ Type, data = dftestwide, theme = 4, main = "Total Fixation Duration by Condition")
pirateplot(formula = TotalFixationDuration ~ Type, data = dfLM[c(dfLM$bedingung == "IN"),], theme = 1, main = "Total Fixation Duration by Type - Indulging")
pirateplot(formula = TotalFixationDuration ~ Type, data = dfLM[c(dfLM$bedingung == "MC"),], theme = 1, main = "Total Fixation Duration by Type - MC")

#ANOVA = ddply(df, c("vpn", "bedingung", "Type"), summarise, pTotalFixationDuration = mean(TotalFixationDuration))
```
```{r}
graph <- dftestwide %>% 
  group_by(Type) %>% summarise(mean.value = mean(value), sd.value = sd(value), se.value = sd(value)/sqrt(n()), n=n())

gp <- ggplot(data = graph,
             aes(x=Type, y=mean.value))
#plot mean values per condition as line
gp <- gp + stat_summary(fun.y = mean, geom="bar", position="dodge")
#set error bars showing 95% CI
#gp <- gp + stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9))
#set error bars showing standard error
gp <- gp + geom_errorbar(aes(ymin=mean.value-se.value, ymax=mean.value+se.value), width = 0.2, position=position_dodge(width=0.90)) 
#set x-axis label
gp <- gp + xlab("Type")
#change position of x-axis label
gp <- gp + theme(axis.title.x = element_text(vjust = 0))
#set y-axis label
gp <- gp + ylab("Diff FixDura MC-IN")
#legend
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
#set title
gp <- gp + ggtitle("böaböa")
#change position of title
gp <- gp + theme(title = element_text(vjust = 1))
#change theme
gp <- gp + theme_bw()
#show plot
gp
```
```{r}
pirateplot(formula = value ~ Type + Picture, data = dftestwide, theme = 2, inf.disp = "bean")
```

### LM Moderator Analysis

- *note that moderator variables are centered at the sample mean for meaningful interpretation of main effects*

#### Anreiz

```{r}
model <- lm(TotalFixationDuration ~ bedingung*Type*anreiz, data=dfLM)
summary(model)
```

#### Commitment

```{r}
model <- lm(TotalFixationDuration ~ bedingung*Type*commitment, data=dfLM)
summary(model)
```

#### Erwartung

```{r}
model <- lm(TotalFixationDuration ~ bedingung*Type*erwartung, data=dfLM)
summary(model)
```

#### Attention

```{r}
model <- lm(TotalFixationDuration ~ bedingung*Type*attention, data=dfLM)
summary(model)
```

#### Free Recall

```{r}
model <- lm(TotalFixationDuration ~ bedingung*Type*freeRecall, data=dfLM)
summary(model)
```
#### Recognition - Hits

```{r}
model <- lm(TotalFixationDuration ~ bedingung*Type*Hits, data=dfLM)
summary(model)
```

# Data Analysis with DiffScores

## simple correlations (Anreiz, Erwartung, Commitment, Attention)

### Line Graphs Displaying Correlations

```{r, fig.width = 12, fig.height = 6}
gp <- ggplot(dfDiff, aes(anreiz, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "pearson")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Anreiz", y=xnameDiff)
gp <- gp + theme_minimal() 
gp

gp <- ggplot(dfDiff, aes(erwartung, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "pearson")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Erwartung", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(commitment, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "pearson")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Commitment", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(attention, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "pearson")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Attention", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(freeRecall, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "pearson")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Free Recall", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  

gp <- ggplot(dfDiff, aes(Hits, TotalFixationDuration, colour=bedingung))
#set scatter plot
gp <- gp + geom_point()
gp <- gp + geom_smooth(method = "lm", aes(fill=bedingung), alpha = 0.1)
#set colour
gp <- gp + scale_color_discrete(name="bedingung")
gp <- gp + scale_colour_manual(values=c("red","dark blue"))
gp <- gp + scale_fill_discrete(name="bedingung")
gp <- gp + scale_fill_manual(values=c("red","dark blue"))
gp <- gp+facet_grid(Order~DiffScore)
gp <- gp + stat_cor(method = "pearson")
gp <- gp + theme(legend.position = "bottom", legend.direction="horizontal")
gp <- gp + labs(x = "Recognition-Hits", y=xnameDiff)
gp <- gp + theme_minimal() 
gp  


```

## Linear Models on Difference Scores

### Fantasy (A) - Neutral (X)

#### Simple Model

```{r}
dfDiffLM <- dfDiffLM[!is.na(dfDiff$TotalFixationDuration),]
dfDiffLM <- dcast(dfDiffLM,  vpn+Picture+bedingung+erwartung+anreiz+commitment+Order+attention+freeRecall+Hits ~ DiffScore, value.var = "TotalFixationDuration", mean)

dfDiffLM$Ax[is.nan(dfDiffLM$Ax)] <- NA

model <- lm(Ax ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(Ax ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(Ax ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(Ax ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(Ax ~ bedingung*Order*attention, data=dfDiffLM)
model5 <- lm(Ax ~ bedingung*Order*freeRecall, data=dfDiffLM)
model6 <- lm(Ax ~ bedingung*Order*Hits, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```

#### Free Recall

```{r}
summary(model5)
```

#### Recognition - Hits

```{r}
summary(model6)
```

### Obstacle (B) - Neutral (X)

#### Simple Model

```{r}
dfDiffLM$Bx[is.nan(dfDiffLM$Bx)] <- NA

model <- lm(Bx ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(Bx ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(Bx ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(Bx ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(Bx ~ bedingung*Order*attention, data=dfDiffLM)
model5 <- lm(Bx ~ bedingung*Order*freeRecall, data=dfDiffLM)
model6 <- lm(Bx ~ bedingung*Order*Hits, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```

#### Free Recall

```{r}
summary(model5)
```

#### Recognition - Hits

```{r}
summary(model6)
```

### Fantasy (A) - Obstacle (B)

#### Simple Model

```{r}
dfDiffLM$AB[is.nan(dfDiffLM$AB)] <- NA

model <- lm(AB ~ bedingung*Order, data=dfDiffLM)
model1 <- lm(AB ~ bedingung*Order*anreiz, data=dfDiffLM)
model2 <- lm(AB ~ bedingung*Order*erwartung, data=dfDiffLM)
model3 <- lm(AB ~ bedingung*Order*commitment, data=dfDiffLM)
model4 <- lm(AB ~ bedingung*Order*attention, data=dfDiffLM)
model5 <- lm(AB ~ bedingung*Order*freeRecall, data=dfDiffLM)
model6 <- lm(AB ~ bedingung*Order*Hits, data=dfDiffLM)

summary(model)
```

#### Anreiz

```{r}
summary(model1)
```

#### Erwartung

```{r}
summary(model2)
```

#### Commitment

```{r}
summary(model3)
```

#### Attention

```{r}
summary(model4)
```

#### Free Recall

```{r}
summary(model5)
```

#### Recognition - Hits

```{r}
summary(model6)
```